\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-13 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
update

\medskip
Here, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics. In order to trigger the formation of fingers, regions with sharp synthetic permeability gradient were introduced. The computational space, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular domain fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeabilities. No-flux boundary conditions were imposed on the upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand face at velocity $u_{1}=1$.

>>>>

\medskip
Here, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics. In order to trigger the formation of fingers, regions with sharp synthetic permeability gradient were introduced. The computational space, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular domain fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeabilities. A no-flux boundary condition was imposed on upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand face at velocity $u_{1}=1$.

Figures \ref{fig:5regions_fixedmesh} and \ref{fig:5regions_adaptmesh} show fluid displacement in simulations performed with fixed and adaptive mesh grids over 1.50 seconds. Both simulations started with a mesh of 13068 triangular elements (\PN[1]{2} element-pairs), however as flow dynamics evolves the number of elements of the simulation conducted with adaptive mesh oscillates from a minimum of 4400 to a maximum of 16430 (Fig.~\ref{fig:5regions_plottimenodeselements})

### 2017-07-13 Papers/ViscousInstabilities/article_figure1.tex
update

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_PlotTimeNodesElements}
\caption{Impact of mesh resolution on flow instabilities: mesh resolution \red{JG: add here some comments ... this pic needs to be placed after the sat plots for the adaptivity case ...}}
\label{fig:5regions_plottimenodeselements}
\end{figure}

>>>>

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
\includegraphics[width=\textwidth]{./Pics1/Section4_4/Five_regions_adapt_PlotTimeNodesElements}
\caption{Impact of mesh resolution on capturing flow instabilities: total number of elements and nodes for simulations performed with fixed and adaptive mesh. }
\label{fig:5regions_plottimenodeselements}
\end{figure}
